InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-02-06 paper.tex

The \textbf{Llama 2} model built and released by Meta. It is available in different sizes, ranging from 7 billion to 70 billion parameters and different appliances like LLAMA 2-Chat, which is optimized for dialogue interaction. When it was released in 2023, it outperformed state-of-the-art open source models. A main refinement compared to its predecessor LLAMA, was the focus on transparency and safety including a post-training alignment. \cite{touvron2023llama}

Another generative model for text is \textbf{BLOOM}. This huge 176 billion parameter big model was published in 2023 and is openly available. The model is multilingual and was built in a decentralized manner by many different contributors. Hundreds of researchers helped with the development of the architecture and tokenizer. The final model was trained on the Jean Zay supercomputer. It is built with a decoder-only architecture and used the ROOTS corpus dataset for training. \cite{workshop2023bloom}

@@

\subsubsection*{Acknowledgments}

@@

\appendix
\section{Appendix}
You may include other additional sections here.

>>>>

@@

\subsubsection*{Acknowledgments}
We would like to thank the "Gesellschaft für Informatik" for providing the competition "Fool AI Detectors". We would also like to thank the teaching assistants of the Foundation Models-Team for their helpful advice.

@@
